PK object batch mode trial

### 2023-06-27 data-raw/batchMode_trial_gpm.Rmd
plot() method now also plots fits

my_ndf %>%
  dplyr::select(Chemical, Species,
                dplyr::all_of(req_vars),
                dplyr::any_of(trans_vars)) %>%
  mutate(Detect = ifelse(Detect, "Detect", "Non-Detect")) %>%
  View()

devtools::load_all()
my_plot <- plot(my_pk)

@@

```{r remaining_methods}
# plot()
# 
# get_tkstats()

>>>>

my_ndf %>%
  dplyr::select(Chemical, Species,
                dplyr::all_of(req_vars),
                dplyr::any_of(trans_vars)) -> my_ndf

# Time interpolation
my_ndf %>% uncount(1) %>% 
  group_by(Dose, Route, Media) %>%
  mutate(Time_trans = (max(Time)/(n() - 1))*(row_number() - 1)) %>%
  View()

devtools::load_all()
my_plot <- plot(my_pk, use_scale_conc = FALSE)

@@

```{r remaining_methods}
# plot()
# coef_sd
# logLik.pk
# get_tkstats()
